Article Title

### 2013-10-04 plos.tex
Kreso's edits

\DeclareMathOperator{\Tr}{tr}
\DeclareMathOperator*{\argmin}{arg\,min}
\newcommand{\mcond}{\,\middle\vert\,}
\newcommand{\cond}{\,\vert\,}
\newcommand{\loss}[1]{\mathcal L\left(#1\right)} 
\newcommand{\T}{\intercal}
\newcommand{\E}[2][]{\mathbb E_{#1}\left[ #2\right]}    % expected value
\newcommand{\TODO}[1]{\emph{\small\color{blue}$\langle\langle$#1$\rangle\rangle$}}
\newcommand*\dif{\mathop{}\,d}
\DeclareMathOperator{\rank}{rank}

@@

% Title must be 150 characters or less
\begin{flushleft}
{\Large
Improved estimates of neural correlations suggest detailed interactions in visual cortex
}
% Insert Author names, affiliations and corresponding author email.
\\
Dimitri Yatsenko$^{1,\ast}$, 
Kre\v{s}imir Josi\'{c}$^{2}$,
Alexander Ecker$^{3,1}$,
Emmanouil Foudarakis$^{1}$,
R.~James Cotton$^{1}$,
Andreas S.~Tolias$^{1}$
\\
\bf{1} Department of Neuroscience, Baylor College of Medicine, Houston, TX, USA
\\
\bf{2} Department of Mathematics and Department of Biology and Biochemistry, University of Houston, Houston, TX, USA
\\
\bf{3} Max Planck Institute of Biological Cybernetics, T\"ubingen, Germany
\\
$\ast$ E-mail: yatsenko@cns.bcm.edu
\end{flushleft}

>>>>

\newcommand{\Kcomment}[1]{{\color{blue}{[KJ: #1]}}}

\DeclareMathOperator{\Tr}{tr}
\newcommand{\mcond}{\,\middle\vert\,}
\newcommand{\cond}{\,\vert\,}
\newcommand{\loss}[1]{\mathcal L\left(#1\right)} 
\newcommand{\T}{\intercal}
\newcommand{\E}[2][]{\mathbb E_{#1}\left[ #2\right]}    % expected value
\newcommand{\TODO}[1]{\emph{\small\color{blue}$\langle\langle$#1$\rangle\rangle$}}
\newcommand*\dif{\mathop{}\,d}
\DeclareMathOperator{\rank}{rank}

@@

% Title must be 150 characters or less
\begin{flushleft}
{\Large
Improved estimates of neural correlations suggest detailed interactions in visual cortex
}
% Insert Author names, affiliations and corresponding author email.
\\
Dimitri Yatsenko$^{1,\ast}$, 
Kre\v{s}imir Josi\'{c}$^{2}$,
Alexander Ecker$^{3,1}$,
Emmanouil Foudarakis$^{1}$,
R.~James Cotton$^{1}$,
Andreas S.~Tolias$^{1}$
\\
\bf{1} Department of Neuroscience, Baylor College of Medicine, Houston, TX, USA
\\
\bf{2} Max Planck Institute of Biological Cybernetics, T\"ubingen, Germany
\\
\bf{3} Department of Mathematics and Department of Biology and Biochemistry, University of Houston, Houston, TX, USA
\\
$\ast$ E-mail: yatsenko@cns.bcm.edu
\end{flushleft}

### 2013-10-04 sections/Estimators.tex
Kreso's edits

A \emph{graphical model} is a multivarate probability distribution with a specified graph of conditional dependencies between its variables \cite{Koller:2009}.  When this distribution is a multivariate normal distribution, the model becomes a \emph{Gaussian graphical model} (GGM) or, equivalently, a \emph{Gaussian Markov Random Field}.  Gaussian graphical models have a straightforward relationship to their covariance matrix $\Sigma$:  Zero elements in the inverse of $\Sigma$ indicate conditional independence between the corresponding pair of variables.

@@

\subsubsection*{Estimator $\mathcal A$: Shrinkage toward diagonal.}
\emph{Estimator $\mathcal A$} shrinks the sample covariance matrix $\hat\Sigma_0$ toward an independent model of the type show in Fig.~\ref{fig:02}A.  The covariance matrix of a GGM in which all units are independent will be diagonal.  
For example, we  could leave the sample variances on the diagonal and zero out the off-diagonal products, making the target estimate 
\begin{equation}\label{eq:sampleVariance}
\hat T= \hat\Sigma_0\circ I
\end{equation}
where $\circ$ denotes the entrywise matrix product (Hadamard product). 
Alternatively, the target could have equal variances, all equal to the average sample variance in the population $v = \frac 1 p \Tr(\hat\Sigma_0)$.
\begin{equation}\label{eq:equalVariance}
\hat T=\frac 1 p \Tr(\hat\Sigma_0) I
\end{equation}
The equal-variance target in Eq.~\ref{eq:equalVariance} has only one degree of freedom and thus lower estimation error but higher bias than the target with sample variances in Eq.~\ref{eq:sampleVariance}. It is not immediately clear which target is better in a particular application. We therefore use the linear mixture of the two targets paramaterized by the mixing coefficient $\alpha\in[0,1]$:
\begin{equation}
\hat T_\alpha = (1-\alpha)(\hat\Sigma_0 \circ I) + \frac \alpha p \mbox{tr}(\hat \Sigma_0)I
\end{equation}
Then the estimator $\hat\Sigma_{\alpha,\lambda}$ is the linear shrinkage of the sample covariance matrix $\hat\Sigma_0$ toward $\hat T_\alpha$ controlled by the mixing proportion $\lambda\in[0,1]$:
\begin{equation}
\hat\Sigma_{\alpha,\lambda} = (1-\lambda)\hat\Sigma_0 + \lambda\hat T_\alpha 
\end{equation}
This covariance matrix estimator is implemented by R's {\tt corpcor} package \cite{Schaefer:2010} and enjoys widespread use in many applications \cite{Schafer:2005}.

@@

@@

The target estimate is then 
\begin{equation}
\hat T_d = \hat L_d + \hat \Psi
\end{equation}
where $\hat L_d$ is a $p\times p$ matrix of rank $d$ and $\hat \Psi$ is a $p\times p$ diagonal matrix. The value of $\hat T_d$ is found by minimizing $\loss{\hat T_d, \hat\Sigma_0}$.

Just as in estimator A, $\hat\Sigma_0$ is shrunk toward $\hat T_d$ by linear mixing controlled by shrinkage intensity $\lambda\in[0,1]$.
\begin{equation}
\hat\Sigma_{d,\lambda} = (1-\lambda)\hat\Sigma_0 + \lambda\hat T_d
\end{equation}
and the optimal values of $d$ and $\lambda$ are found by cross-validation within the training set.

Factor analysis has a rich history of testing hypotheses about the dominance of a few common inputs \cite{findagoodone}.  In neuroscience, the hypothesis that the population activity in small local circuits is largely driven by a few latent factors has been investigated \cite{Yu:2009,Ecker:2013}.  Estimation of covariance matrices by shrinkage toward a factor model has been used in finance for portfolio risk assessment \cite{Ledoit:2003,Fan:2008}.

@@

For Gaussian Graphical Models, zeros in the inverse covariance matrix indicate statisitcal independence between the corresponding pairs. Thus the inverse covariance matrix $S=-\Sigma^{-1}$ is also the adjacency matrix of the GGM, indicating which pairs are conditionally dependent. \TODO{discuss how quickly (or slowly) this breaks down with deviations from gaussianity, e.g.~MaxEnt models, Ising models.} \TODO{Also, motivate this from the perpsective of linear regression as in \cite{Varoquaux:2012}.} The off-diagonal elements of $S$ are proportional to partial pairwise correlations between corresponding pairs of neurons. \TODO{Expand.} Regularization of covariance matrix estimation by sparsifying the inverse of the estimate has been using in function genomics \cite{Schafer:2005,other} and fMRI functional connectivity \cite{Varoquaux:2012}.

The covariance matrix estimate is then 
\begin{equation}
-\hat\Sigma_\rho^{-1} =\arg\min\limits_S \loss{-S^{-1},\hat\Sigma_0}  \quad \mbox{such that} \quad  \|S_\rho\|_0 = \rho
\end{equation}
where $S_\rho$ is a sparse matrix with $\rho$ non-zero coefficients. $\|S\|_0$ denotes the number of non-zero elements of matrix $S$.
Solving this approximation in this form is computationally challenging. The problem can be made computationally tractable by replacing the $L_0$ norm with the $L_1$ norm, which converts the problem into one of convex optimization \cite{Donoho:2000}.  The resulting algorithm, known as \emph{graphical lasso} or \emph{GLASSO}  \cite{Meinshausen:2006,Yuan:2007,Banerjee:2008,Friedman:2008}, produces the following estimator  
\begin{equation}
-\hat\Sigma_\lambda^{-1} = \arg\min\limits_S \loss{-S^{-1},\hat\Sigma_0} + \lambda \|S\|_1
\end{equation}
where $\lambda \|S\|_1$ is the $L_1$ norm of the matrix. \TODO{clarify}.

Just as in the previous estimators, the optimal value of the regularization parameter $\lambda$ is found from training data by cross-validation.

\subsubsection*{Estimator $\mathcal D$: Sparse inverse + low-rank}
\emph{Estimator $\mathcal D$} produces a low-dimensional estimate by finding an apprxomation of $\hat\Sigma_0$ approximating the sample covariance matrix such that its inverse is the sum of a spase matrix and a low-rank matrix. Covariance matrices of this form correspond to Gaussian graphical models of the form depicted in Fig.~\ref{fig:02}D.

The inverse $S=-\Sigma^{-1}$ of the covariance matrix of a GGM constitutes the graph of conditional dependencies (interactions) between the units.  With the assumption of sparse organization of interactions in the network, $S$ is assumed to be sparse.  When the observed units are part of a larger GGM that includes other latent units, let the negative inverse $S^*$ of the joint distribution of both observed and latent units be composed of four partitions
\begin{equation}
S^* = 
\begin{pmatrix}
S_{11} & S_{12} \\
S_{12}^\T & S_{22} 
\end{pmatrix}
\end{equation}
where partition $S_{11}$ describes the interactions between the visible units, $S_{12}$ describe the interactions between visible and latent units, and $S_{22}$ describes the interactions between the latent units. 
Then the covariance matrix of between the observed unit is 
\begin{equation}
\Sigma = -\left(S_{11} - S_{12}S_{22}^{-1}S_{12}^\T\right)^{-1}
\end{equation} 
The rank of matrix $S_{12}S_{22}^{-1}S_{12}$ equals the number of latent units. Rather than solving for the precise dependency structure with and between latent units in matrices $S_{12}$ and $S_{22}$, we simply replace the matrix $- S_{12}S_{22}^{-1}S_{12}$ with on low-rank matrix $L_d=- S_{12}S_{22}^{-1}S_{12}$ with rank $d$.

>>>>

A \emph{graphical model} is a multivarate probability distribution with a specified graph of conditional dependencies between its variables \cite{Koller:2009}.  When this distribution is a multivariate normal distribution, the model becomes a \emph{Gaussian graphical model} (GGM) or, equivalently, a \emph{Gaussian Markov Random Field}.  Gaussian graphical models have a straightforward relationship to their covariance matrix $\Sigma$:  Zero elements in the inverse of $\Sigma$ indicate conditional independence between the corresponding pair of variables.  
\Kcomment{It may be important to note that we are not fitting Gaussian graphical models, however.}

@@

\subsubsection*{Estimator $\mathcal A$: Shrinkage toward diagonal.}
\emph{Estimator $\mathcal A$} shrinks the sample covariance matrix $\hat\Sigma_0$ toward that of the independent model shown in Fig.~\ref{fig:02}A.  The covariance matrix of a GGM in which all units are independent will be diagonal.  
For example, we  could leave the sample variances on the diagonal set the off-diagonal terms to zero. The target estimate
is then 
\begin{equation}\label{eq:sampleVariance}
\hat T= \hat\Sigma_0\circ I
\end{equation}
where $\circ$ denotes the entrywise matrix product (Hadamard product). 
Alternatively, the target could be a diagonal matrix with all variances equal to the average sample variance, $v = \frac 1 p \Tr(\hat\Sigma_0)$, so that
\begin{equation}\label{eq:equalVariance}
\hat T=\frac 1 p \Tr(\hat\Sigma_0) I
\end{equation}
The equal-variance target in Eq.~\ref{eq:equalVariance} has only one degree of freedom and thus lower estimation error but higher bias than the target with sample variances in Eq.~\ref{eq:sampleVariance}. It is not immediately clear which target is better in a particular application. We therefore use the linear mixture of the two targets paramaterized by the mixing coefficient $\alpha\in[0,1]$,
\begin{equation}
\hat T_\alpha = (1-\alpha)(\hat\Sigma_0 \circ I) + \frac \alpha p \mbox{tr}(\hat \Sigma_0)I.
\end{equation}
The estimator $\hat\Sigma_{\alpha,\lambda}$ is the linear shrinkage of the sample covariance matrix $\hat\Sigma_0$ toward $\hat T_\alpha$ controlled by the mixing proportion $\lambda\in[0,1]$,
\begin{equation}
\hat\Sigma_{\alpha,\lambda} = (1-\lambda)\hat\Sigma_0 + \lambda\hat T_\alpha.
\end{equation}
This covariance matrix estimator is implemented by R's {\tt corpcor} package \cite{Schaefer:2010} and is used widely~\cite{Schafer:2005}.

@@

\Kcomment{Yes -- you give no details about the cross-validation.  You should provide some details at least in 
one case, or have a separate section that discusses how you implemented it.}

@@

The target estimate is then 
\begin{equation}
\hat T_d = \hat L_d + \hat \Psi
\end{equation}
where $\hat L_d$ is a $p\times p$ matrix of rank $d$ and $\hat \Psi$ is a $p\times p$ diagonal matrix. The value of $\hat T_d$ is found by minimizing $\loss{\hat T_d, \hat\Sigma_0}$. 
\Kcomment{I would give a more explicit representation of $\hat L_d$ as a product to show that the factors can be understood as common input.}

As with estimator A, $\hat\Sigma_0$ is shrunk toward $\hat T_d$ by linear mixing controlled by shrinkage intensity $\lambda\in[0,1]$,
\begin{equation}
\hat\Sigma_{d,\lambda} = (1-\lambda)\hat\Sigma_0 + \lambda\hat T_d,
\end{equation}
and the optimal values of $d$ and $\lambda$ are found by cross-validation within the training set.

Factor analysis has long been used to test hypotheses about the dominance of a few common inputs \cite{findagoodone}.  In neuroscience, the hypothesis that the population activity in small local circuits is largely driven by a few latent factors has been investigated \cite{Yu:2009,Ecker:2013}.  Estimation of covariance matrices by shrinkage toward a factor model has been used in finance for portfolio risk assessment \cite{Ledoit:2003,Fan:2008}.

@@

For Gaussian Graphical Models, zeros in the inverse covariance matrix indicate statistical independence between the corresponding pairs. Thus the inverse covariance matrix $S=-\Sigma^{-1}$ is also the adjacency matrix of the GGM, indicating which pairs are conditionally dependent. \TODO{discuss how quickly (or slowly) this breaks down with deviations from gaussianity, e.g.~MaxEnt models, Ising models.} \TODO{Also, motivate this from the perpsective of linear regression as in \cite{Varoquaux:2012}.}  \Kcomment{This is a bit confusing -- in the first sentence, you have statistical independence, in the second, you talk about conditional independence.  You want to emphasize that a 0 inverse means that -- in the GGM -- the two nodes only ``talk'' indirectly through other nodes.} The off-diagonal elements of $S$ are proportional to partial pairwise correlations between corresponding pairs of neurons. \TODO{Expand.} Regularization of covariance matrix estimation by sparsifying the inverse of the estimate has been using in function genomics \cite{Schafer:2005,other} and fMRI functional connectivity \cite{Varoquaux:2012}.

The covariance matrix estimate is then 
\begin{equation}
-\hat\Sigma_\rho^{-1} =\arg\min\limits_S \loss{-S^{-1},\hat\Sigma_0}  \quad \mbox{such that} \quad  \|S_\rho\|_0 = \rho
\end{equation}
where $S_\rho$ is a sparse matrix with $\rho$ non-zero coefficients. $\|S\|_0$ denotes the number of non-zero elements of matrix $S$.
Solving this approximation in this form is computationally challenging. The problem can be made computationally tractable by replacing the $L_0$ norm with the $L_1$ norm, which converts the problem into one of convex optimization \cite{Donoho:2000}.  The resulting algorithm, known as \emph{graphical lasso} or \emph{GLASSO}  \cite{Meinshausen:2006,Yuan:2007,Banerjee:2008,Friedman:2008}, produces the following estimator  
\begin{equation}
-\hat\Sigma_\lambda^{-1} = \arg\min\limits_S \loss{-S^{-1},\hat\Sigma_0} + \lambda \|S\|_1
\end{equation}
where $\lambda \|S\|_1$ is the $L_1$ norm of the matrix. \TODO{clarify}. \Kcomment{Yes - at least define the norm, if you are already taking about it. No need to expand a lot more, though.}

Just as in the previous estimators, the optimal value of the regularization parameter $\lambda$ is found from training data by cross-validation. \Kcomment{I would say this up front, so you don't have to repeat it.  Again, I think more details about cross-validation should be given.}

\subsubsection*{Estimator $\mathcal D$: Sparse inverse + low-rank}
\emph{Estimator $\mathcal D$} produces a low-dimensional estimate by finding an approximation of $\hat\Sigma_0$ approximating the sample covariance matrix such that its inverse is the sum of a spase matrix and a low-rank matrix. Covariance matrices of this form correspond to Gaussian graphical models of the form depicted in Fig.~\ref{fig:02}D.

The inverse $S=-\Sigma^{-1}$ of the covariance matrix of a GGM constitutes the graph of conditional dependencies (interactions) between the units.  With the assumption of sparse organization of interactions in the network, $S$ is assumed to be sparse.  When the observed units are part of a larger GGM that includes other latent units, let the negative inverse $S^*$ of the joint distribution of both observed and latent units be composed of four partitions
\begin{equation}
S^* = 
\begin{pmatrix}
S_{11} & S_{12} \\
S_{12}^\T & S_{22} 
\end{pmatrix}
\end{equation}
where partition $S_{11}$ describes the interactions between the visible units, $S_{12}$ describe the interactions between visible and latent units, and $S_{22}$ describes the interactions between the latent units. 
Then the covariance matrix of between the observed unit is 
\begin{equation}
\Sigma = -\left(S_{11} - S_{12}S_{22}^{-1}S_{12}^\T\right)^{-1}
\end{equation} 
The rank of matrix $S_{12}S_{22}^{-1}S_{12}$ equals the number of latent units. Rather than solving for the precise dependency structure with and between latent units in matrices $S_{12}$ and $S_{22}$, we simply replace the matrix $- S_{12}S_{22}^{-1}S_{12}$ with a low-rank matrix $L_d=- S_{12}S_{22}^{-1}S_{12}$ with rank $d$.

### 2013-10-04 sections/Regularization.tex
Kreso's edits

The unbiased estimator $\hat\Sigma_0$ makes $\bar\Sigma=\Sigma$ and thereby minimizes approximation error, but may be excessively susceptible to sample noise and result in high estimation error.

The estimator risk can be reduced by \emph{regularization}. Regularization is the deliberate biasing (\emph{``shrinkage''}) of the estimate toward a low-dimensional, less variable \emph{target estimate} \cite{Bickel:2006,Ledoit:2004}. 
A regularized estimator solves the bias-variance tradeoff to produce a biased but less variable estimates aiming to minimize the estimator's risk.  
Various regularization schemes focus on the dimensionality reduction part \TODO{rephrase} by selecting the optimal target estimate from a family of estimates with reduced dimensionality \cite{findit}.  
Other estimators only shrink the sample covariance matrix toward a single target estimator \cite{Schafer:2005}. 
Yet other regularizers effectively combine shrinkage and dimensionality reduction \cite{findit}.

>>>>

An unbiased estimator, such as the sample covariance,  $\hat\Sigma_0,$ makes $\bar\Sigma=\Sigma$ and thereby minimizes approximation error, but may be excessively susceptible to sample noise and result in high estimation error.

The estimator risk can be reduced by \emph{regularization} -- a deliberate biasing (\emph{``shrinkage''}) of the estimate toward a low-dimensional, less variable \emph{target estimate} \cite{Bickel:2006,Ledoit:2004}. 
A regularized estimator solves the bias-variance tradeoff to produce a biased but less variable estimate to minimize the estimator's risk.  
Various regularization schemes focus on the dimensionality reduction part \TODO{rephrase} by selecting the optimal target estimate from a family of estimates with reduced dimensionality \cite{findit}.  
Other estimators only shrink the sample covariance matrix toward a single target estimator \cite{Schafer:2005}. 
Yet other regularizers effectively combine shrinkage and dimensionality reduction \cite{findit}.

### 2013-10-04 sections/Theory.tex
Kreso's edits

For more rigorous notation, definitions, and derivations, see Appendix.

@@

The sample covariance matrix is constructed to be unbiased, such that $\E{\hat\Sigma_0} = \Sigma$.

\subsection*{Evaluation of covariance matrix estimators}
The quality of a covariance matrix estimate $\hat\Sigma$ is measured by a real-valued \emph{loss function} $\loss{\hat\Sigma,\Sigma}$.  The loss function quantifies the deviation of $\hat\Sigma$ from $\Sigma$ and attains its minimum  when $\hat\Sigma = \Sigma$.

@@

The aim of our project is to produce covariance matrix estimates that minimize the expected loss 
\begin{equation}
r = \E{\loss{\hat\Sigma, \Sigma}}
\end{equation}
which is know as the \emph{risk} of $\hat\Sigma$.

In practice, the true value $\Sigma$ is not accessible and estimators' risks must be estimated from the data.  This may be accomplished through \emph{validation}. 
Let $\hat\Sigma_0^\prime$ denote a sample covariance matrix measured from an independent sample that was not used included in the computation of $\hat\Sigma$.

$\loss{\cdot,\cdot}$ is additive in its second argument such that
 \begin{equation}\label{eq:additivity}
 \loss{\hat\Sigma,X_1} + \loss{\hat\Sigma,X_2} \equiv \loss{\hat\Sigma,X_1+X_2}
 \end{equation}
Then \emph{validation loss}  \TODO{check appropriate term}
\begin{equation}\label{eq:validationLoss}
\hat \ell = \loss{\hat\Sigma,\hat\Sigma_0^\prime}
\end{equation}
is an unbiased estimate of the risk:
 \begin{equation}\label{eq:empiricalRisk}
\E[(\hat\Sigma, \hat\Sigma_0^\prime)] {\hat\ell} 
= \E[(\hat\Sigma, \hat\Sigma_0^\prime)]{\loss{\hat\Sigma,\hat\Sigma_0^\prime}}
= \E{\loss{\hat\Sigma,\E{\hat\Sigma_0^\prime}}}
= \E{\loss{\hat\Sigma,\Sigma}} = r
 \end{equation}
Therefore, estimators resulting in consistently lower validation loss can be inferred to produce estimates that are closer to truth than estimators with higher validation loss.

>>>>

For detailed explanation of the notation, definitions, and derivations, see Appendix.

@@

The sample covariance matrix is constructed to be unbiased, so that $\E{\hat\Sigma_0} = \Sigma$.

\subsection*{Evaluation of covariance matrix estimators}
The quality of a covariance matrix estimate $\hat\Sigma$ is measured by a real-valued \emph{loss function} $\loss{\hat\Sigma,\Sigma}$.  The loss function quantifies the deviation of $\hat\Sigma$ from $\Sigma$ and attains its minimum  when $\hat\Sigma = \Sigma$.  \Kcomment{Could we say that it quantifies the error in the estimate?}

@@

The aim of our project is to produce covariance matrix estimates that minimize the expected loss 
\begin{equation}
r = \E{\loss{\hat\Sigma, \Sigma}}
\end{equation}
which is known as the \emph{risk} of $\hat\Sigma$.

In practice, the true value $\Sigma$ is not accessible and an estimators' risks must be estimated from the data.  This may be accomplished through \emph{validation}.  \Kcomment{If you will discuss validation later, point to it.}
Let $\hat\Sigma_0^\prime$ denote a sample covariance matrix measured from an independent sample that was not used included in the computation of $\hat\Sigma$.

$\loss{\cdot,\cdot}$ is additive in its second argument so that \Kcomment{You frequently use ``such that'' instead of ``so that''}
 \begin{equation}\label{eq:additivity}
 \loss{\hat\Sigma,X_1} + \loss{\hat\Sigma,X_2} \equiv \loss{\hat\Sigma,X_1+X_2}
 \end{equation}
Then \emph{validation loss}  \TODO{check appropriate term}
\begin{equation}\label{eq:validationLoss}
\hat \ell = \loss{\hat\Sigma,\hat\Sigma_0^\prime}
\end{equation}
is an unbiased estimate of the risk:
 \begin{equation}\label{eq:empiricalRisk}
\E[(\hat\Sigma, \hat\Sigma_0^\prime)] {\hat\ell} 
= \E[(\hat\Sigma, \hat\Sigma_0^\prime)]{\loss{\hat\Sigma,\hat\Sigma_0^\prime}}
= \E{\loss{\hat\Sigma,\E{\hat\Sigma_0^\prime}}}
= \E{\loss{\hat\Sigma,\Sigma}} = r
 \end{equation}
Therefore, estimators resulting in consistently lower validation loss can be inferred to produce estimates that are closer to truth than estimators with higher validation loss.
\Kcomment{This is probably not a very insightful question -- but why do we assume that the sample covariance
is what we compare $\hat\Sigma$ when we validate the results.  Our point is that this estimate is not very good.}
